---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

Welcome to my first workflowr project.

```{r}
data <- read.csv("data/OldFaithful_geyser.csv")
```

The data shows average eruption length (in minutes) of each of 272 geysers in the Old Faithful at the Yellowstone National Park, WY,  on the first column and average wait time (also in minutes) between each eruption. Let's take a look at top portion of the data. And compute descriptive statistics for each column.

```{r}
head(data)
summary(data)
```

Let's plot distributions for each column and a scatterplot to see if they show any correlation.
```{r}
hist(data$X.Eruption.length..mins.., main="Histogram of Eruption length")
hist(data$Eruption.wait..mins.., main="Histogram of Eruption wait")
```

It looks like both variables have bimodal distribution. Let's see if these two bimodal distributions are correlated.
```{r}
plot(data$X.Eruption.length..mins..,data$Eruption.wait..mins..,xlab = "Eruption Length (min)", ylab = "Eruption wait time (min)")
```

It looks like they are highly correlated. Let's do a linear regression to quantify the fit.

```{r}
fit <- lm(Eruption.wait..mins.. ~ X.Eruption.length..mins.., data = data)
summary(fit)
```

How close the datapoints to the fitted line? As our r-squared number, `r summary(fit)$r.squared` , shows, they are pretty close to the fitted line, suggesting a strong positive correlation between Eruption wait time and Eruption length. 

