---
title: "Home"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---

Welcome to my first workflowr project.

```{r}
data <- read.csv("data/OldFaithful_geyser.csv")
```

The data shows average eruption length (in minutes) of each of 272 geysers in the Old Faithful on the first column and average time between each eruption. Let's take a look at top portion of the data. And compute descriptive statistics for each column.

```{r}
head(data)
summary(data)
```

Let's plot distributions for each column and a scatterplot to see if they show any correlation.
```{r}
hist(data$X.Eruption.length..mins.., main="Histogram of Eruption length")
hist(data$Eruption.wait..mins.., main="Histogram of Eruption wait")
```

It looks like both variables have bimodal distribution. Let's see if these two bimodal distributions are correlated.
```{r}
plot(data$X.Eruption.length..mins..,data$Eruption.wait..mins..,xlab = "Eruption Length (min)", ylab = "Eruption wait time (min)")
```


